[WIP] Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religous Marriage Ceremonies in England and Wales

### 2024-04-24 paper/paper.qmd
paper update

## Limitations

>>>>

## Limitations
Despite this paper's effort to highlight how marriage ceremony data can be a reflection of the religious attitudes in England and Wales, there are some limitations that must be addressed.

While the marriage ceremony data does seem to corroborate the overall decline of citizens identifying as religious, the marriage data might be slightly skewed in the population demographics that it collects from. As stated in research from King's College London, 48% of Baby Boomers expressed a belief in God in comparison to Gen Z at 37% in the United Kingdom [@ukreligion]. It is evident that there are differences in religiosity between generations, therefore it is possible that the marriage data could be skewed towards a decline of religiosity since those of ages more likely to marry belong to younger age generations such as Millenials and Gen Z's.
